%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage{color,hyperref}
\usepackage{color,soul}
\usepackage{comment} 
\usepackage{paralist}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.1}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}

%______________________________________________________________________________________________________________________
\begin{document}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\name{\Large \textsf{Rasool Ahmad}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    Postdoctoral Fellow \\
    (SNSF Early Postdoc Mobility Fellow) \hfill e-mail: {\href{mailto:rasool@stanford.edu}{\nolinkurl{rasool@stanford.edu}}} \\
    \href{https://micronano.stanford.edu/}{Micro and Nano Mechanics Group} \hfill e-mail: {\href{mailto:rasoolahmad.a@gmail.com}{\nolinkurl{rasoolahmad.a@gmail.com}}} \\
    \href{https://me.stanford.edu/}{Department of Mechanical Engineering} \hfill Mobile: +1 408 384 2528 \\
    \href{https://www.stanford.edu/}{Stanford University} \hfill OrcID:  0000-0002-4154-6902 \\
    CA 94305, USA  \hfill Google Scholar: {\href{https://scholar.google.ch/citations?user=ujjgd08AAAAJ&hl=en}{\nolinkurl{ujjgd08AAAAJ}}}

    %\line(1,0){440}



    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Computational materials science, dislocation mechanics, atomistic simulation, plasticity, machine learning for science

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{\href{https://www.epfl.ch/en/}{\textsf{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne,
                Switzerland} }} \\
    \text{Ph.D.  in Mechanics} \hfill \small{Aug 1, 2016 - Oct 30, 2020} \\
    Advisor:  \href{https://people.epfl.ch//william.curtin?lang=en}{Dr. William Curtin}

    \textbf{\href{http://www.iitk.ac.in/}{\textsf{Indian Institute of Technology, Kanpur, India}}}\vspace{0mm}\\
    \text{B.Tech.-M.Tech. Dual Degree in Mechanical Engineering} \hfill \small{Jul 15, 2011 - Jul 15, 2016}
    \vspace{0cm}
    % \begin{compactitem}
    % \item[-] {Cumulative Performance Index (M.Tech.) - \textbf{10} (on a scale of 10)}
    % \item[-] {Cumulative Performance Index (B.Tech.) - \textbf{8.2} (on a scale of 10)}
    % \end{compactitem}%__________________________________________________________________________________________________________________
    % Honours and Awards

    \section{\mysidestyle Select Awards and Honors}  \vspace{0mm}

    Recipient of the \textbf{Early Postdoctoral Mobility Fellowship} (2021-2022) awarded by the Swiss National Science Foundation.

    \vspace{-0.3cm}
    Selected for the \textbf{Humboldt Postdoctoral Research Fellowship} (2021).

    \vspace{-0.3cm}
    Received the \textbf{Best Ph.D. Thesis Award} by EDME (Mechanics) doctoral program, EPFL (2021).

    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}
    \small{\textit{Total citations: 516} (Google Scholar, Sep 2022)}

    \href{https://iopscience.iop.org/article/10.1088/1361-651X/ac7f4b} {\textbf{R. Ahmad}, and W.~Cai, ``Free energy calculation of crystalline solids using normalizing flows", \textit{Model. Simul. Mater. Sci. Eng.} 30 (2022) 065007}

    \href{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.101.022503} {\textbf{R. Ahmad}, S. Paul and S.~Basu, ``Characterization of entanglements in glassy polymeric ensembles using the Gaussian linking number", \textit{Phys. Rev. E} 101 (2020) 022503.}

    \href{https://www.sciencedirect.com/science/article/pii/S1359645419307256} {\textbf{R. Ahmad}, Z. Wu and W.~A.
        Curtin, ``Analysis of double cross-slip of pyramidal I $\langle \boldsymbol{c} + \boldsymbol{a} \rangle$ screw dislocations and implications for ductility in Mg alloys", \textit{Acta Mater.} 183 (2020) 228-241.}

    \href{https://www.sciencedirect.com/science/article/pii/S1359645419302198} {\textbf{R. Ahmad}, B. Yin, Z. Wu and W.~A. Curtin, ``Designing high ductility in magnesium alloys", \textit{Acta Mater.} 172 (2019) 161-184.}

    \href{https://www.sciencedirect.com/science/article/pii/S1359646218303804}{\textbf{R. Ahmad}, Z. Wu, S. Groh and W.~A. Curtin, ``Pyramidal II to basal transformation of $\langle \boldsymbol{c} + \boldsymbol{a} \rangle$ edge dislocations in Mg-Y alloys", \textit{Scr. Mater.} 155 (2018) 114-118.}

    \href{https://iopscience.iop.org/article/10.1088/1361-651X/aacfd2}{\textbf{R. Ahmad}, S. Groh, M. Ghazisaeidi and W.~A. Curtin, ``Modified embedded-atom method interatomic potential for Mg-Y alloys", \textit{Model. Simul. Mater. Sci. Eng.} 26 (2018) 065010.}

    \href{https://science.sciencemag.org/content/359/6374/447.full} {Z. Wu, \textbf{R. Ahmad}, B. Yin, S Sandlöbes and W.~A. Curtin, ``Mechanistic origin and prediction of enhanced ductility in magnesium alloys", \textit{Science} 359 (2018) 447-452.}

    %-------------------------------------------------------------------------------------------------------------
    % Submited to journals

    \section{\mysidestyle Manuscripts submitted}

    \href{https://arxiv.org/pdf/2208.02320.pdf} {\textbf{R. Ahmad}, M.~Liu, M.~Ortiz, T.~Mukerji, and W.~Cai, ``Computation of effective elastic moduli of rocks using hierarchical homogenization", submitted to \textit{J. Mech. Phys. Solids}, arXiv preprint \textit{arXiv:2208.02320}}

    \href{https://www.essoar.org/pdfjs/10.1002/essoar.10512161.1} {M.~Liu, \textbf{R. Ahmad}, W.~Cai, and T.~Mukerji, ``Hierarchical homogenization with deep-learning-based surrogate model for rapid estimation of effective permeability from digital rocks", submitted to \textit{J. Geophys. Research - Solid Earth}, eossoar priprint \textit{essoar.10512161.1}}



    \clearpage
    %__________________________________________________________________________________________________________________
    % Conferences
    \section{\mysidestyle Conference}

    \textbf{R. Ahmad}, and W. Cai, ``Free energy calculation of crystalline defects using normalizing flows'', \textit{Multiscale Materials Modeling (MMM)} (2022) Baltimore, MD, USA

    \textbf{R. Ahmad}, and W. Cai, ``Free energy calculation of crystalline solids using normalizing flows'', \textit{Materials Research Society (MRS) Spring Meeting} (2022) Honolulu, USA

    \textbf{R. Ahmad}, Z. Wu, and W.~A. Curtin, ``Pyramidal $\langle \boldsymbol{c} + \boldsymbol{a} \rangle$ cross-slip mediated ductility in Mg alloys ductility", \textit{The Minerals, Metals \& Materials Society (TMS)} (2020) San Diego, USA.

    W.~A. Curtin, \textbf{R. Ahmad}, B. Yin and Z. Wu, ``Design of Ductile Rare-Earth-Free Magnesium Alloys", \textit{Magnesium Technology 2020}, 19-24

    \textbf{R. Ahmad}, Z. Wu, S. Groh and W.~A. Curtin, ``Pyramidal II to basal transformation of $\langle
        \boldsymbol{c} + \boldsymbol{a} \rangle$ edge dislocations in Mg-Y alloys and its implication for
    ductility", \textit{Euromat} (2019) Stockholm, Sweden.

    % \textit{Mechanics and Physics of Stretchable Objects} (2018) Corsica, France.

    %______________________
    % Honours and Awards
    \section{\mysidestyle Research Experiences}
    \textbf{\textsf{Postdoctoral Fellow}}    \hfill  \small{May 1, 2021 - current} \\
    Swiss National Science Foundation (SNSF) Early Postdoc Mobility Fellow for the project titled \textit{Investigation into finite temperature atomic-scale crystal plasticity through generative deep learning}.\\
    \href{https://micronano.stanford.edu/}{Micro and Nano Mechanics Group}, \\
    \href{https://www.stanford.edu/}{Stanford University, California, USA}\\
    Advisor:  \href{https://web.stanford.edu/~caiwei/}{Dr. Wei Cai}


    % \textbf{\textsf{Postdoctoral Researcher}}    \hfill  \small{Nov 1, 2020 - April 30, 2021} \\
    % \href{https://lammm.epfl.ch/}{Laboratory for Multiscale Mechanics Modeling}, \\
    % \href{https://www.epfl.ch/en/}{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland}\\
    % Advisor:  \href{https://people.epfl.ch//william.curtin?lang=en}{Dr. William Curtin}


    \textbf{\textsf{Graduate Student Researcher (Ph.D.)}}    \hfill  \small{Aug 1, 2016 - Oct 30, 2020} \\
    \href{https://infoscience.epfl.ch/record/280981}{\textit{Atomic Scale Investigations into the Origins of Ductility in Mg Alloys}}\\
    \href{https://www.epfl.ch/en/}{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland}\\
    Advisor:  \href{https://people.epfl.ch//william.curtin?lang=en}{Dr. William Curtin}


    \textbf{\textsf{Graduate Student Researcher (M.Tech.)}} \hfill \small{Jul 15, 2015 - Jul 15, 2016} \\
    \textit{Investigation into disentanglement of polymer chains in a glassy amorphous polymer through molecular dynamics simulations}   \\
    \href{http://www.iitk.ac.in/}{Indian Institute of Technology, Kanpur, India}\\
    Advisor: \href{http://home.iitk.ac.in/~sbasu/}{Dr. Sumit Basu}

    %----------------------
    %--- services ---------

    \section{\mysidestyle Services}
    - Referee services for journals \\
    \hspace*{0.5cm} Acta Materialia, and CALPHAD: Computer Coupling of Phase Diagrams and Thermochemistry

    - Session-chair in conferences \\
    \hspace*{0.5cm} Multiscale Materials Modeling, 2022, Baltimore, MD, USA


    \section{\mysidestyle Academic Projects}

    Kinetic Monte Carlo simulation of screw dislocation mobility in BCC metals  \hfill \small{Feb - Jun 2019}

    \vspace{-0.3cm}
    Updated Lagrangian Finite Element Formulation  \hfill \small{Aug - Nov 2014}

    \vspace{-0.3cm}
    Static Equilibrium of a Red Blood Cell \hfill \small{Aug - Nov 2014}

    \vspace{-0.3cm}
    Minimum Energy Path of a Reaction Using Nudge Elastic Band Method \hfill \small{Jan - Apr 2014}


    %\line(1,0){440}


    %______________________________________________________________________________________________________________________
    \section{\mysidestyle Select Courses}

    \begin{tabular}{@{}p{7.5cm}p{7.5cm}}
        - Computational Multiscale Modeling of Solid & - Molecular Modeling in Chemistry              \\
        - Nature and Properties of Materials         & -  Non-Linear Finite Element Method            \\
        - Fracture mechanics                         & - Finite Element Method                        \\
        - Theory of Elasticity                       & - Advanced Mechanics of Solid                  \\
        - Mechanics of Biological Membrane           & - Wave Propagation in Elastic Solid            \\
        - Non-Linear Vibration                       & -	Rheology and Structure of Complex Fluids      \\
        - Topics in Topology                         & - Vibration and Control                        \\
        - Linear Algebra and Ordinary Diff Eqns      & - Complex Analysis and Partial Diff Eqns       \\
        - Real Analysis and Calculus                 & - Fourier Analysis and Boundary Value Problems
    \end{tabular}

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Technical \\Skills}
    \textbf{\textsf{Programming Languages}} - Python, C, C++,  FORTRAN, Matlab

    \textbf{\textsf{Software}} -  LAMMPS, ParaDis, Ovito, Abaqus, Gaussian
    %---------------------------------------------------------------------------------
    % Teaching experience	

    \clearpage
    \section{\mysidestyle Teaching \\Experiences}

    \textbf{\textsf{Teaching Assistant, EPFL}} \textsf{(Four semesters)}
    \vspace{-0.3cm}\begin{compactitem}
        \item[-] Solid Mechanics \hfill \small{Spring  Semesters 2018, 2019, 2020}
        \item[-] Introduction to Structural Mechanics  \hfill \small{Spring  Semester 2017}
    \end{compactitem}

    \textbf{\textsf{Teaching Assistant, IIT Kanpur}} \textsf{(Two semesters)}
    \vspace{-0.3cm}\begin{compactitem}
        \item[-] Basic Electrical Engineering \hfill \small{Fall  Semesters 2016}
        \item[-] Engineering Graphics and Design  \hfill \small{Spring  Semester 2015}
    \end{compactitem}



    %\line(1,0){440}
    %__________________________________________________________________________________________________________________
    % Computer Skills

    % \section{\mysidestyle Positions of Responsibility}
    % \textbf{\textsf{Academic Mentor}}, Counseling Service Team`12, IIT Kanpur \hfill \small{Aug 2012 - Apr 2013}

    % \vspace{-0.3cm}
    % \textbf{\textsf{Account Secretary}}, Hall Executive Committee, Hall 3,  IIT Kanpur \hfill \small{Aug 2012 - Apr 2013}
    ­%%%
    %%%

    \section{\mysidestyle References}
    \begin{minipage}[t]{0.5\textwidth}
        \href{https://web.stanford.edu/~caiwei/}{\textbf{\textsf{Wei Cai}}}\\
        Professor\\
        Department of Mechanical Engineering\\
        Stanford University, USA \\
        caiwei@stanford.edu\\[1em]
        \href{https://scholars.cityu.edu.hk/en/persons/zhaoxuan-wu(32022051-be5f-44e8-84eb-794d8f78d35c).html}{\textbf{\textsf{Zhaoxuan Wu}}}\\
        Assistance Professor\\
        Department of Materials Science and Engineering\\
        City University of Hong Kong, China\\
        zhaoxuwu@cityu.edu.hk\\[1em]
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
        \href{https://people.epfl.ch//william.curtin?lang=en}{\textbf{\textsf{William Curtin}}}\\
        Professor\\
        Institute of Mechanical Engineering\\
        EPFL, Switzerland\\
        william.curtin@epfl.ch\\[1em]
        \href{http://home.iitk.ac.in/~sbasu/}{\textbf{\textsf{Sumit Basu}}}\\
        Professor\\
        Department of Mechanical Engineering\\
        Indian Institute of Technology (IIT) Kanpur, India\\
        sbasu@iitk.ac.in\\[1em]
    \end{minipage}

\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
